### 2022-12-16 chapter1/chapter1.tex
Added missing_trim figure to supplement and reference in main text

Though the phylo-HMM removed phylogenetically incongruent ``insertions,'' some sequences still contained extensive segments of uninterrupted gaps. These segments are easily identified in regions which are otherwise highly conserved, so they are also likely the result of incorrect or incomplete annotations. Unfortunately, they can also span more diverged regions, which complicates a simple rule- or threshold-based approach for identifying them. Thus, another phylo-HMM was trained to label each position in a sequence as generated by either a ``missing'' or ``not missing'' state. In this case, however, the aligned sequences were processed individually and not as aligned columns. As the previous phylo-HMM already ensured each column has sufficient support, these labels can instead be used to exclude sequences from downstream analyses depending on the amount of tolerated overlap with the regions of interest.

>>>>

Though the phylo-HMM removed phylogenetically incongruent ``insertions,'' some sequences still contained extensive segments of uninterrupted gaps. These segments are easily identified in regions which are otherwise highly conserved, so they are also likely the result of incorrect or incomplete annotations. However, they can also span more diverged regions, which complicates a simple rule- or threshold-based approach for identifying them. Thus, another phylo-HMM was trained to label each position in a sequence as generated by either a ``missing'' or ``not missing'' state. In this case, though, the aligned sequences were processed individually and not as aligned columns. As the previous phylo-HMM already ensured each column has sufficient support, these labels can instead be used to exclude sequences from downstream analyses depending on the amount of tolerated overlap with the regions of interest. Overall, 15\% of alignments have at least one sequence with a segment of ``missing'' data (Fig.~\ref{sfig:missing_trim}).

### 2022-12-16 chapter1/chapter1_supporting.tex
Added missing_trim figure to supplement and reference in main text

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{missing_trim/out/missing_trim.png}
\centering
\caption{\textbf{Missing phylo-HMM trimming details.}
\textbf{(A)} Most alignments have no sequences with ``missing'' segments. \textbf{(B)} Of the alignments with sequences trimmed of missing segments, a majority have only one trimmed sequence. \textbf{(C-D)} The length of missing segments can vary considerably, both in terms of the number of positions as well as its ratio to the number of columns in the alignment.}
\label{sfig:missing_trim}
\end{figure}
